Verifying Demonstrations

### 2021-06-16 paper/current-crowd-counting.tex
Breaks out outline, CANSifies intro
Removes ref on voting properties due to Doug's comments

We draw inspiration from properties for voting systems as formalized
in ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that their vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
The eligibility requirement is slightly different as for protests it must also
include temporal %\footnote{%
%   Elections also have some temporal aspects, such that one cannot vote at any 
%   time and a vote in one election should not be reusable in the next election.
%   However, the temporal relation for a protest is not as strictly defined as for 
%   elections as a protest can start at any time and last for an arbitrary period 
%   of time.%
% }
and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
(This is the difference to a petition.)

In ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}, the main three
privacy properties for voting protocols are given as:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove their vote was cast in any particular way.
\end{description}

>>>>

We draw inspiration from properties for voting systems:
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
  \item[Individual verifiability:] each voter can verify that their vote is 
    included in the result.
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
The eligibility requirement is slightly different as for protests it must also
include temporal %\footnote{%
%   Elections also have some temporal aspects, such that one cannot vote at any 
%   time and a vote in one election should not be reusable in the next election.
%   However, the temporal relation for a protest is not as strictly defined as for 
%   elections as a protest can start at any time and last for an arbitrary period 
%   of time.%
% }
and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
(This is the difference to a petition.)

The main three privacy properties for voting protocols are given as:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove their vote was cast in any particular way.
\end{description}
